\begin{rubric}{Professional Experience}{

  \entry*[2016]
  \textbf{\href{http://www.sds.sc.gov.br/Secretaria do Estado}
    - IT Management}

  \textbf{Position:} Intern.

  \textbf{Responsabilities:} Support in controlling the hardware inventory,
  installation and configuration of computers and other equipments,
  provide assistance to staff members regarding technology issues,
  manage the used softwares, perform back-ups.


  \entry*[2014]
  \textbf{\href{http://www.comissariaromar.com.br/}{Comissária Romar}
    - Customs Brokerage}

  \textbf{Position:} Intern.

  \textbf{Responsabilities:} Assist in operational Responsabilities
   related to customs clearance, such as document analysis,
   freight forwarding, tax classification, registration of
   Declaration of Importation, Registration of Export, Declaration of
   Export, Import License and customs inspection. Support the
   financial sector.

  \entry*[2013 - 2014]
  \textbf{\href{http://www.ufsc.br/}{UFSC} - Patrimonial Management
    Department}

  \textbf{Position:} Intern.

  \textbf{Responsabilities:} Transport logistics; Corporate business
   service; conferencing and controlling material stocks;
   conferencing and control of entry and exit of the material in storage;
   support for organizational planning activities; producing
   official documents.


  \entry*[2012 - 2013]
  \textbf{\href{http://www.fiesc.com.br/}{FIESC} - COI Sector}

  \textbf{Position:} Intern.

  \textbf{Responsabilities:} Assist in the participation and organization of
   meetings of the energy, logistics and environment boards, assist
   in research; help controling, monitoring and filling
   spreadsheets; assist in the preparation of charts and organizing
   files.

}\end{rubric}

